---
title: "RADAR-base pRMT report"
author: "Pedro F Zuccolo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '/Users/pedrozuccolo/Desktop/maayAppAnalyses/')
```
#Packages
```{r}
library(haven)
library(tidyverse)
library(lubridate)

```


# MAAY

Maio 2022: fiz acordo com a The Hyve que incluía 

"Hi Pedro, I just spoke to Nivethika. I think we have a plan. We'd definitely like to support you setting up RADAR-base -- part of our goal is trying to get others to take up use of the platform, we have a small pot of person-hours available for pro bono work. I think as you are already well underway to getting setup this would be a good case for us to give you some final support to get to a starting point for your project.
I think Nivethika has suggested getting setup on K3S on AWS?
In return, we would ask that Hyve https://www.thehyve.nl/ and King's College Maudsley Biomedical Research Centre are acknowledged on academic output https://maudsleybrc.nihr.ac.uk/research/acknowledging-the-brc/. Also we might ask that you perhaps would be willing to write a short blog post on the work on the https://radar-base.org website?"



* Periods of data collection
* incidents
  ** system shutdown


```{r}
#period of data collection
install_dates <- read_dta("data/data_aggregated/motherly_rct_2021_t1_t2_t3_app_6_12_2022.dta")

typeof(install_dates$t0_data_recrut)

install_dates$t0_data_recrut <- as.Date(install_dates$t0_data_recrut)

# Filter for dates after 2022-06-13 and before 2022-11-19
app_offered_to <- install_dates %>%
  filter(t0_data_recrut > as.Date("2022-06-13") & t0_data_recrut < as.Date("2022-08-30"))

nrow(app_offered_to)
```

```{r}
reasons_for_not_using <- read_dta("data/data_raw/motherly_rct_2021_monitoria_10_10_2023.dta")

view(reasons_for_not_using)

table(reasons_for_not_using$instalacao_2)

```
